Notes on the Godunov Step in {\tt MAESTRO} and {\tt VARDEN}

### 2008-04-17 docs/Godunov_notes/paper.tex
cleaning up the notation so it is crystal clear what we are doing
Merging notes on enthalpy_pred_type into main document to remove some of the tables at the end.

\def\half  {\frac{1}{2}}
\def\dt    {\Delta t}

@@

For the x-faces, the 1D extrapolation of $u$ is:
\begin{eqnarray}
u_L^{\trans} &=& u_{\ib-\eb_x}^n + \left(\half - \frac{\dt}{2h}u_{\ib-\eb_x}^n\right)\Delta_x u_{\ib-\eb_x}^n, \\
u_R^{\trans} &=& u_{\ib}^n - \left(\half + \frac{\dt}{2h}u_{\ib}^n\right)\Delta_x u_{\ib}^n.
\end{eqnarray}
We pick the final edge states using a Riemann solver:
\begin{equation}
u^{\trans}_{\ib-\half\eb_x} =
\begin{cases}
0, & \left(u_L^{\trans} \le 0 ~ {\rm AND} ~ u_R^{\trans} \ge 0\right) ~ {\rm OR} ~ \left|u_L^{\trans} + u_R^{\trans}\right| < \epsilon, \\
u_L^{\trans}, & u_L^{\trans} + u_R^{\trans} > 0, \\
u_R^{\trans}, & u_L^{\trans} + u_R^{\trans} < 0, \\
\end{cases}
\end{equation}
For the r-faces, we choose include the radial derivative terms proportional to $w_0$ and $(\Ubt\cdot\eb_r) = \wt$.  The term proportional to $w_0$ is included by using $w$ rather than $\wt$ as the advection speed.  The term proportional to $\wt$ is an additional term.  For the r-faces, the 1D extrapolation of $\wt$ is:
\begin{eqnarray}
\wt_L^{\trans} &=& \wt_{\ib-\eb_r}^n + \left(\half - \frac{\dt}{2h}w_{\ib-\eb_r}^n\right)\Delta_r \wt_{\ib-\eb_r}^n - \frac{\dt}{2}\wt_{\ib-\eb_r}^n\left(\frac{\partial w_0}{\partial r}\right)_{\ib-\eb_r},\label{Radial utrans_L} \\
\wt_R^{\trans} &=& \wt_{\ib}^n - \left(\half + \frac{\dt}{2h}w_{\ib}^n\right)\Delta_r \wt_{\ib}^n - \frac{\dt}{2}\wt_{\ib}^n\left(\frac{\partial w_0}{\partial r}\right)_{\ib}.\label{Radial utrans_R}
\end{eqnarray}
The total radial velocity is defined as:
\begin{equation}
w_{\ib}^n = \wt_{\ib}^n + \frac{w_{0,r+\half}+w_{0,r-\half}}{2}.\label{Total Radial Velocity}
\end{equation}
The spatial derivatives of $w_0$ are given by the two-point centered difference:
\begin{equation}
\left(\frac{\partial w_0}{\partial r}\right)_{\ib} = \frac{w_{0,r+\half}-w_{0,r-\half}}{h}.\label{Radial Derivative of w_0}
\end{equation}
We pick the final edge states using:
\begin{equation}
\wt^{\trans}_{\ib-\half\eb_r} =
\begin{cases}
0, & \left(w_L^{\trans} \le 0 ~ {\rm AND} ~ w_R^{\trans} \ge 0\right) ~ {\rm OR} ~ \left|w_L^{\trans} + w_R^{\trans}\right| < \epsilon, \\
\wt_L^{\trans}, & w_L^{\trans} + w_R^{\trans} > 0, \\
\wt_R^{\trans}, & w_L^{\trans} + w_R^{\trans} < 0, \\
\end{cases}
\end{equation}
where $w_L^{\trans} = \wt_L^{\trans} + w_{0,r-\half}$ and $w_R^{\trans} = \wt_R^{\trans} + w_{0,r-\half}$.  Finally, we call {\tt addw0} to compute $w^{\trans}$ from $\wt^{\trans}$.
\subsection{3D Cartesian Case}
For the rest of this paper, for 3D Cartesian problems, $\Ub = (u,v,w)$ and $\Ubt = (u,v,\wt)$.  We will use the shorthand $\ib = (x,y,r)$.\\

The only difference between the 2D and 3D Cartesian cases is that we must also compute $v^{\trans}$.  The procedure is analogous to computing $u^{\trans}$.  For y-faces, the 1D extrapolation of $v$ is:
\begin{eqnarray}
v_L^{\trans} &=& v_{\ib-\eb_y}^n + \left(\half - \frac{\dt}{2h}v_{\ib-\eb_y}^n\right)\Delta_y v_{\ib-\eb_y}^n, \\
v_R^{\trans} &=& v_{\ib}^n - \left(\half + \frac{\dt}{2h}v_{\ib}^n\right)\Delta_y v_{\ib}^n,
\end{eqnarray}
\begin{equation}
v^{\trans}_{\ib-\half\eb_y} =
\begin{cases}
0, & \left(v_L^{\trans} \le 0 ~ {\rm AND} ~ v_R^{\trans} \ge 0\right) ~ {\rm OR} ~ \left|v_L^{\trans} + v_R^{\trans}\right| < \epsilon, \\
v_L^{\trans}, & v_L^{\trans} + v_R^{\trans} > 0, \\
v_R^{\trans}, & v_L^{\trans} + v_R^{\trans} < 0. \\
\end{cases}
\end{equation}
\subsection{3D Spherical Case}
For the rest of this paper, for 3D spherical problems, $\Ub = (u,v,w)$ and $\Ubt = (\ut,\vt,\wt)$.  We will use the shorthand $\ib = (x,y,z)$.\\

@@

The force terms are:
\begin{equation}
\fb =
\left(\begin{array}{c}
f_u \\
f_w \\
\end{array}\right)
= \frac{1}{\rho}\nabla\pi + \frac{1}{\rho_0}\frac{\partial\pi_0}{\partial r}\eb_r - \frac{(\rho-\rho_0)}{\rho}g\eb_r.\label{Force Term}
\end{equation}
\subsection{2D Cartesian Case}
We begin by computing a time-centered 1D extrapolation of $u$ to r-faces:
\begin{eqnarray}
u_L^{1D} &=& u_{\ib-\eb_r}^n + \left(\half - \frac{\dt}{2h}w_{\ib-\eb_r}^n\right)\Delta_r u_{\ib-\eb_r}^n, \\
u_R^{1D} &=& u_{\ib} - \left(\half + \frac{\dt}{2h}w_{\ib}^n\right)\Delta_r u_{\ib}^n.
\end{eqnarray}
Then we upwind based on $w^{\trans}$:
\begin{equation}
u_{\ib-\half\eb_r}^{1D} =
\begin{cases}
\half\left(u_L^{1D} + u_R^{1D}\right), & \left|w^{\trans}_{\ib-\half\eb_r}\right| < \epsilon \\
u_L^{1D}, & w^{\trans}_{\ib-\half\eb_r} > 0, \\
u_R^{1D}, & w^{\trans}_{\ib-\half\eb_r} < 0. \\
\end{cases}
\end{equation}
Then, we do a full-dimensional extrapolation of $u$ to x-faces:
\begin{eqnarray}
u_L^{\mac} &=& u_{\ib-\eb_x}^n + \left(\half - \frac{\dt}{2h}u_{\ib-\eb_x}\right)\Delta_x u_{\ib-\eb_x}^n + \frac{\dt}{2}f_{u,\ib-\eb_x} \nonumber \\
&& - \frac{\dt}{4h}\left(w_{\ib-\eb_x+\half\eb_r}^{\trans}+w_{\ib-\eb_x-\half\eb_r}^{\trans}\right)\left(u_{\ib-\eb_x+\half\eb_r}^{1D} - u_{\ib-\eb_x-\half\eb_r}^{1D}\right), \\
u_R^{\mac} &=& u_{\ib}^n - \left(\half + \frac{\dt}{2h}u_{\ib}\right)\Delta_x u_{\ib}^n + \frac{\dt}{2}f_{u,\ib} \nonumber \\
&& - \frac{\dt}{4h}\left(w_{\ib+\half\eb_r}^{\trans}+w_{\ib-\half\eb_r}^{\trans}\right)\left(u_{\ib+\half\eb_r}^{1D} - u_{\ib-\half\eb_r}^{1D}\right).
\end{eqnarray}
Finally, we solve a Riemann problem:
\begin{equation}
u_{\ib-\half\eb_x}^{\mac,*} =
\begin{cases}
0, & \left(u_L^{\mac} \le 0 ~ {\rm AND} ~ u_R^{\mac} \ge 0\right) ~ {\rm OR} ~ \left|u_L^{\mac} + u_R^{\mac}\right| < \epsilon, \\
u_L^{\mac}, & u_L^{\mac} + u_R^{\mac} > 0, \\
u_R^{\mac}, & u_L^{\mac} + u_R^{\mac} < 0. 
\end{cases}
\end{equation}

To compute $\wt^{\mac,*}$, we use an analogous procedure for computing $u^{\mac,*}$, except that we need to incorporate the terms in equation (\ref{Perturbational Velocity Equation}) proportional to $w_0$ and $\partial w_0/\partial r$ into the full-dimensional extrapolation.  We compute a time-centered 1D extrapolation of $\wt$ to x-faces:
\begin{eqnarray}
\wt_L^{1D} &=& \wt_{\ib-\eb_x}^n + \left(\half - \frac{\dt}{2h}u_{\ib-\eb_x}^n\right)\Delta_x \wt_{\ib-\eb_x}^n, \\
\wt_R^{1D} &=& \wt_{\ib} - \left(\half + \frac{\dt}{2h}u_{\ib}^n\right)\Delta_x \wt_{\ib}^n.
\end{eqnarray}
Then we upwind based on $u^{\trans}$:
\begin{equation}
\wt_{\ib-\half\eb_x}^{1D} =
\begin{cases}
\half\left(\wt_L^{1D} + \wt_R^{1D}\right), & \left|u^{\trans}_{\ib-\half\eb_x}\right| < \epsilon \\
\wt_L^{1D}, & u^{\trans}_{\ib-\half\eb_x} > 0, \\
\wt_R^{1D}, & u^{\trans}_{\ib-\half\eb_x} < 0. \\
\end{cases}
\end{equation}
Then, we do a full-dimensional extrapolation of $\wt$ to r-faces, incorporating the extra term proportional to $w_0$ by using $w$ instead of $\wt$ as the advection velocity and the extra term proportional to $\partial w_0/\partial r$ as a separate term:
\begin{eqnarray}
\wt_L^{\mac} &=& \wt_{\ib-\eb_r}^n + \left(\half - \frac{\dt}{2h}w_{\ib-\eb_r}\right)\Delta_r \wt_{\ib-\eb_r}^n + \frac{\dt}{2}f_{w,\ib-\eb_r} \nonumber \\
&& - \frac{\dt}{4h}\left(u_{\ib+\half\eb_x-\eb_r}^{\trans}+u_{\ib-\half\eb_x-\eb_r}^{\trans}\right)\left(\wt_{\ib+\half\eb_x-\eb_r}^{1D} - \wt_{\ib-\half\eb_x-\eb_r}^{1D}\right) \nonumber \\
&& - \frac{\dt}{2h}\wt_{\ib-\eb_r}(w_{0,j-\half} - w_{0,j-\frac{3}{2}}),\label{wt_L Extrapolation} \\
\wt_R^{\mac} &=& \wt_{\ib}^n - \left(\half + \frac{\dt}{2h}w_{\ib}\right)\Delta_r \wt_{\ib}^n + \frac{\dt}{2}f_{w,\ib} \nonumber \\
&& - \frac{\dt}{4h}\left(u_{\ib+\half\eb_x}^{\trans}+u_{\ib-\half\eb_x}^{\trans}\right)\left(\wt_{\ib+\half\eb_x}^{1D} - \wt_{\ib-\half\eb_x}^{1D}\right) \nonumber \\
&& - \frac{\dt}{2h}\wt_{\ib}(w_{0,j+\half} - w_{0,j-\half}).\label{wt_R Extrapolation}
\end{eqnarray}
Next, we solve a Riemann problem:
\begin{equation}
\wt_{\ib-\half\eb_r}^{\mac,*} =
\begin{cases}
0, & \left(w_L^{\mac} \le 0 ~ {\rm AND} ~ w_R^{\mac} \ge 0\right) ~ {\rm OR} ~ \left|w_L^{\mac} + w_R^{\mac}\right| < \epsilon, \\
\wt_L^{\mac}, & w_L^{\mac} + w_R^{\mac} > 0, \\
\wt_R^{\mac}, & w_L^{\mac} + w_R^{\mac} < 0. 
\end{cases}
\end{equation}
Finally, we call {\tt addw0} to compute $\Ub^{\mac,*}$ from $\Ubt^{\mac,*}$.
\subsection{3D Cartesian Case}
\subsection{3D Spherical Case}
\cleardoublepage
\section{Computing $\rho^{'\edge}, X_k^{\edge}, h^{\edge},$ and $T^{\edge}$ in {\tt MAESTRO}}
In {\tt scalar\_advance}, we call {\tt make\_edge\_scal} to compute $\rho^{'\edge}, X_k^{\edge}, h^{\edge},$ and $T^{\edge}$ at each edge.  The procedure is the same for each scalar, so we shall simply denote the scalar as $s$. \\

@@

f_h &=& \frac{1}{\rho}\left(\psi + (\Ubt\cdot\eb_r)\frac{\partial p_0}{\partial r} \right), \\
f_T &=& \frac{1}{\rho c_p}\left\{(1-\rho h_p)\left[\psi + (\Ubt\cdot\eb_r)\frac{\partial p_0}{\partial r}\right] - \sum_k\rho\xi_k\dot\omega_k + \rho H_{\rm nuc} + \rho H_{\rm ext}\right\}.

@@

\subsection{3D Cartesian Case}
\subsection{3D Spherical Case}

>>>>

\def\half  {\frac{1}{2}}
\def\dt    {\Delta t}
\def\kth   {k_{\rm th}}

@@

For the x-faces, the 1D extrapolation of $u$ is:
\begin{eqnarray}
u_{L,\ib-\half\eb_x}^{\trans} &=& u_{\ib-\eb_x}^n + \left(\half - \frac{\dt}{2h}u_{\ib-\eb_x}^n\right)\Delta_x u_{\ib-\eb_x}^n, \\
u_{R,\ib-\half\eb_x}^{\trans} &=& u_{\ib}^n - \left(\half + \frac{\dt}{2h}u_{\ib}^n\right)\Delta_x u_{\ib}^n.
\end{eqnarray}
We pick the final edge states using a Riemann solver:
\begin{equation}
u^{\trans}_{\ib-\half\eb_x} =
\begin{cases}
0, & \left(u_{L,\ib-\half\eb_x}^{\trans} \le 0 ~ {\rm AND} ~ u_{R,\ib-\half\eb_x}^{\trans} \ge 0\right) ~ {\rm OR} ~ \left|u_{L,\ib-\half\eb_x}^{\trans} + u_{R,\ib-\half\eb_x}^{\trans}\right| < \epsilon, \\
u_{L,\ib-\half\eb_x}^{\trans}, & u_{L,\ib-\half\eb_x}^{\trans} + u_{R,\ib-\half\eb_x}^{\trans} > 0, \\
u_{R,\ib-\half\eb_x}^{\trans}, & u_{L,\ib-\half\eb_x}^{\trans} + u_{R,\ib-\half\eb_x}^{\trans} < 0, \\
\end{cases}
\end{equation}
For the r-faces, we choose include the radial derivative terms proportional to $w_0$ and $(\Ubt\cdot\eb_r) = \wt$.  The term proportional to $w_0$ is included by using $w$ rather than $\wt$ as the advection speed.  The term proportional to $\wt$ is an additional term.  For the r-faces, the 1D extrapolation of $\wt$ is:
\begin{eqnarray}
\wt_{L,\ib-\half\eb_r}^{\trans} &=& \wt_{\ib-\eb_r}^n + \left(\half - \frac{\dt}{2h}w_{\ib-\eb_r}^n\right)\Delta_r \wt_{\ib-\eb_r}^n - \frac{\dt}{2}\wt_{\ib-\eb_r}^n\left(\frac{\partial w_0}{\partial r}\right)_{\ib-\eb_r},\label{Radial utrans_L} \\
\wt_{R,\ib-\half\eb_r}^{\trans} &=& \wt_{\ib}^n - \left(\half + \frac{\dt}{2h}w_{\ib}^n\right)\Delta_r \wt_{\ib}^n - \frac{\dt}{2}\wt_{\ib}^n\left(\frac{\partial w_0}{\partial r}\right)_{\ib}.\label{Radial utrans_R}
\end{eqnarray}
The total radial velocity is defined as:
\begin{equation}
w_{\ib}^n = \wt_{\ib}^n + \frac{w_{0,r+\half}+w_{0,r-\half}}{2}.\label{Total Radial Velocity}
\end{equation}
The spatial derivatives of $w_0$ are given by the two-point centered difference:
\begin{equation}
\left(\frac{\partial w_0}{\partial r}\right)_{\ib} = \frac{w_{0,r+\half}-w_{0,r-\half}}{h}.\label{Radial Derivative of w_0}
\end{equation}
We pick the final edge states using:
\begin{equation}
\wt^{\trans}_{\ib-\half\eb_r} =
\begin{cases}
0, & \left(w_L^{\trans} \le 0 ~ {\rm AND} ~ w_R^{\trans} \ge 0\right) ~ {\rm OR} ~ \left|w_L^{\trans} + w_R^{\trans}\right| < \epsilon, \\
\wt_{L,\ib-\half\eb_r}^{\trans}, & w_L^{\trans} + w_R^{\trans} > 0, \\
\wt_{R,\ib-\half\eb_r}^{\trans}, & w_L^{\trans} + w_R^{\trans} < 0, \\
\end{cases}
\end{equation}
where $w_L^{\trans} = \wt_{L,\ib-\half\eb_r}^{\trans} + w_{0,r-\half}$ and $w_R^{\trans} = \wt_{R,\ib-\half\eb_r}^{\trans} + w_{0,r-\half}$.  Finally, we call {\tt addw0} to compute $w^{\trans}$ from $\wt^{\trans}$.
\subsection{3D Cartesian Case}
For the rest of this paper, for 3D Cartesian problems, $\Ub = (u,v,w)$ and $\Ubt = (u,v,\wt)$.  We will use the shorthand $\ib = (x,y,r)$.\\

The only difference between the 2D and 3D Cartesian cases is that we must also compute $v^{\trans}$.  The procedure is analogous to computing $u^{\trans}$.  For y-faces, the 1D extrapolation of $v$ is:
\begin{eqnarray}
v_{L,\ib-\half\eb_y}^{\trans} &=& v_{\ib-\eb_y}^n + \left(\half - \frac{\dt}{2h}v_{\ib-\eb_y}^n\right)\Delta_y v_{\ib-\eb_y}^n, \\
v_{R,\ib-\half\eb_y}^{\trans} &=& v_{\ib}^n - \left(\half + \frac{\dt}{2h}v_{\ib}^n\right)\Delta_y v_{\ib}^n,
\end{eqnarray}
\begin{equation}
v^{\trans}_{\ib-\half\eb_y} =
\begin{cases}
0, & \left(v_{L,\ib-\half\eb_y}^{\trans} \le 0 ~ {\rm AND} ~ v_{R,\ib-\half\eb_y}^{\trans} \ge 0\right) ~ {\rm OR} ~ \left|v_{L,\ib-\half\eb_y}^{\trans} + v_{R,\ib-\half\eb_y}^{\trans}\right| < \epsilon, \\
v_{L,\ib-\half\eb_y}^{\trans}, & v_{L,\ib-\half\eb_y}^{\trans} + v_{R,\ib-\half\eb_y}^{\trans} > 0, \\
v_{R,\ib-\half\eb_y}^{\trans}, & v_{L,\ib-\half\eb_y}^{\trans} + v_{R,\ib-\half\eb_y}^{\trans} < 0. \\
\end{cases}
\end{equation}
\subsection{3D Spherical Case}
For the rest of this paper, for 3D spherical problems, $\Ub = (u,v,w)$ and $\Ubt = (\ut,\vt,\wt)$.  We will use the shorthand $\ib = (x,y,z)$.\\

@@

The force terms are:
\begin{equation}
\fb =
\left(\begin{array}{c}
f_u \\
f_w \\
\end{array}\right)
= \frac{1}{\rho}\nabla\pi + \frac{1}{\rho_0}\frac{\partial\pi_0}{\partial r}\eb_r - \frac{(\rho-\rho_0)}{\rho}g\eb_r.\label{Force Term}
\end{equation}
\subsection{2D Cartesian Case}
We begin by computing a time-centered 1D extrapolation of $u$ to r-faces:
\begin{eqnarray}
u_{L,\ib-\half\eb_r}^{1D} &=& u_{\ib-\eb_r}^n + \left(\half - \frac{\dt}{2h}w_{\ib-\eb_r}^n\right)\Delta_r u_{\ib-\eb_r}^n, \\
u_{R,\ib-\half\eb_r}^{1D} &=& u_{\ib} - \left(\half + \frac{\dt}{2h}w_{\ib}^n\right)\Delta_r u_{\ib}^n.
\end{eqnarray}
Then we upwind based on $w^{\trans}$:
\begin{equation}
u_{\ib-\half\eb_r}^{1D} =
\begin{cases}
\half\left(u_{L,\ib-\half\eb_r}^{1D} + u_{R,\ib-\half\eb_r}^{1D}\right), & \left|w^{\trans}_{\ib-\half\eb_r}\right| < \epsilon \\
u_{L,\ib-\half\eb_r}^{1D}, & w^{\trans}_{\ib-\half\eb_r} > 0, \\
u_{R,\ib-\half\eb_r}^{1D}, & w^{\trans}_{\ib-\half\eb_r} < 0. \\
\end{cases}
\end{equation}
Then, we do a full-dimensional extrapolation of $u$ to x-faces:
\begin{eqnarray}
u_{L,\ib-\half\eb_x}^{\mac} &=& u_{\ib-\eb_x}^n + \left(\half - \frac{\dt}{2h}u_{\ib-\eb_x}\right)\Delta_x u_{\ib-\eb_x}^n + \frac{\dt}{2}f_{u,\ib-\eb_x} \nonumber \\
&& - \frac{\dt}{4h}\left(w_{\ib-\eb_x+\half\eb_r}^{\trans}+w_{\ib-\eb_x-\half\eb_r}^{\trans}\right)\left(u_{\ib-\eb_x+\half\eb_r}^{1D} - u_{\ib-\eb_x-\half\eb_r}^{1D}\right), \\
u_{R,\ib-\half\eb_x}^{\mac} &=& u_{\ib}^n - \left(\half + \frac{\dt}{2h}u_{\ib}\right)\Delta_x u_{\ib}^n + \frac{\dt}{2}f_{u,\ib} \nonumber \\
&& - \frac{\dt}{4h}\left(w_{\ib+\half\eb_r}^{\trans}+w_{\ib-\half\eb_r}^{\trans}\right)\left(u_{\ib+\half\eb_r}^{1D} - u_{\ib-\half\eb_r}^{1D}\right).
\end{eqnarray}
Finally, we solve a Riemann problem:
\begin{equation}
u_{\ib-\half\eb_x}^{\mac,*} =
\begin{cases}
0, & \left(u_{L,\ib-\half\eb_x}^{\mac} \le 0 ~ {\rm AND} ~ u_{R,\ib-\half\eb_x}^{\mac} \ge 0\right) ~ {\rm OR} ~ \left|u_{L,\ib-\half\eb_x}^{\mac} + u_{R,\ib-\half\eb_x}^{\mac}\right| < \epsilon, \\
u_{L,\ib-\half\eb_x}^{\mac}, & u_{L,\ib-\half\eb_x}^{\mac} + u_{R,\ib-\half\eb_x}^{\mac} > 0, \\
u_{R,\ib-\half\eb_x}^{\mac}, & u_{L,\ib-\half\eb_x}^{\mac} + u_{R,\ib-\half\eb_x}^{\mac} < 0. 
\end{cases}
\end{equation}

To compute $\wt^{\mac,*}$, we use an analogous procedure for computing $u^{\mac,*}$, except that we need to incorporate the terms in equation (\ref{Perturbational Velocity Equation}) proportional to $w_0$ and $\partial w_0/\partial r$ into the full-dimensional extrapolation.  We compute a time-centered 1D extrapolation of $\wt$ to x-faces:
Then, we do a full-dimensional extrapolation of $\wt$ to r-faces, incorporating the extra term proportional to $w_0$ by using $w$ instead of $\wt$ as the advection velocity and the extra term proportional to $\partial w_0/\partial r$ as a separate term:
\wt_{L,\ib-\half\eb_r}^{\mac} &=& \wt_{\ib-\eb_r}^n + \left(\half - \frac{\dt}{2h}w_{\ib-\eb_r}\right)\Delta_r \wt_{\ib-\eb_r}^n + \frac{\dt}{2}f_{w,\ib-\eb_r} \nonumber \\
&& - \frac{\dt}{2h}\wt_{\ib-\eb_r}(w_{0,j-\half} - w_{0,j-\frac{3}{2}}),\label{wt_L Extrapolation} \\
\wt_{R,\ib-\half\eb_r}^{\mac} &=& \wt_{\ib}^n - \left(\half + \frac{\dt}{2h}w_{\ib}\right)\Delta_r \wt_{\ib}^n + \frac{\dt}{2}f_{w,\ib} \nonumber \\
&& - \frac{\dt}{2h}\wt_{\ib}(w_{0,j+\half} - w_{0,j-\half}).\label{wt_R Extrapolation}
Next, we solve a Riemann problem:
\wt_{\ib-\half\eb_r}^{\mac,*} =
0, & \left(w_L^{\mac} \le 0 ~ {\rm AND} ~ w_R^{\mac} \ge 0\right) ~ {\rm OR} ~ \left|w_L^{\mac} + w_R^{\mac}\right| < \epsilon, \\
\wt_{L,\ib-\half\eb_r}^{\mac}, & w_L^{\mac} + w_R^{\mac} > 0, \\
\wt_{R,\ib-\half\eb_r}^{\mac}, & w_L^{\mac} + w_R^{\mac} < 0. 
Finally, we call {\tt addw0} to compute $\Ub^{\mac,*}$ from $\Ubt^{\mac,*}$.
%\subsection{3D Cartesian Case}
%\subsection{3D Spherical Case}
\section{Computing $\rho^{'\edge}, X_k^{\edge}, h^{\edge},$ and $T^{\edge}$ in {\tt MAESTRO}}
In {\tt scalar\_advance}, we call {\tt make\_edge\_scal} to compute $\rho^{'\edge}, X_k^{\edge}, h^{\edge},$ and $T^{\edge}$ at each edge.  The procedure is the same for each scalar, so we shall simply denote the scalar as $s$.  We always need to compute $\rho'$ and $X_k$ to edges.
\begin{itemize}
\item For {\tt enthalpy\_pred\_type} = 1, we predict $(\rho h)'$ to edges.
\item For {\tt enthalpy\_pred\_type} = 2, we predict $h$ to edges.
\item For {\tt enthalpy\_pred\_type} = 3 and 4, we predict $T$ to edges.
\end{itemize}

@@

f_{(\rho h)'} &=& (\Ubt\cdot\eb_r)\frac{\partial p_0}{\partial r} -(\rho h)'\nabla\cdot\Ub^{\mac} - \nabla\cdot\left[(\rho h)_0\Ubt^{\mac}\right] + \nabla\cdot\kth\nabla T \\
f_h &=& \frac{1}{\rho}\left(\psi + (\Ubt\cdot\eb_r)\frac{\partial p_0}{\partial r} + \nabla\cdot\kth\nabla T \right), \\
f_T &=& \frac{1}{\rho c_p}\left\{(1-\rho h_p)\left[\psi + (\Ubt\cdot\eb_r)\frac{\partial p_0}{\partial r}\right] - \sum_k\rho\xi_k\dot\omega_k + \rho H_{\rm nuc} + \rho H_{\rm ext} + \nabla\cdot\kth\nabla T \right\}.

@@

%\subsection{3D Cartesian Case}
%\subsection{3D Spherical Case}
